dbRDA analysis

### 2017-08-18 doc/RMD/RDA-analysis.Rmd
Update manuscript to auto-generate results
I also added a comment on data availability and
a comment on the low value of rd in CA

```{r marginal_anova, cache = TRUE}
anova(cap11cc, by = "margin")
anova(cap16cc, by = "margin")
```

@@

```{r total_anova2, cache = TRUE}
anova(cap11cc2)
```

@@

```{r marginal_anova2, cache = TRUE}
anova(cap11cc2, by = "margin")
```

@@

>>>>

```{r marginal_anova, cache = TRUE}
set.seed(2017-08-17)
(cap11anova <- anova(cap11cc, by = "margin"))
set.seed(2017-08-17)
(cap16anova <- anova(cap16cc, by = "margin"))
```

@@

```{r total_anova2, cache = TRUE}
set.seed(2017-08-17)
anova(cap11cc2)
```

@@

```{r marginal_anova2, cache = TRUE}
set.seed(2017-08-17)
(cap11anova2 <- anova(cap11cc2, by = "margin"))
```

@@

## Saving Data

These data are important for reporting in the manuscript and expensive to 
generate, so I will save them here

```{r save_data}
save(cap11cc, cap11cc2, 
     cap11sum, cap11sum2, 
     cap11anova, cap11anova2,
     file = file.path("data", "RDA_results.rda"))
```
